---
title: 'Regression Discontinuity Analysis of Bikeshare in Montreal'
author: "Daniel Fuller (dfuller@mun.ca)"
date: "January, 2017"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

```{r, echo=FALSE, warning=FALSE}
options(scipen = 2, digits=4)
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE, tidy = TRUE, comment=NA)
```

```{r, echo=FALSE, warning=FALSE}
library(dplyr)
library(foreign)
library(ggplot2)
library(car)
library(rdrobust)
library(RCurl)
library(doBy)
library(psych)
library(extrafont)
library(dplyr)
rd1 <- read.dta("bixi_rd_2012_08_28.dta")
bixinbhd <- read.dta("SR_2006_il_montreal.dta")
rd <- merge(rd1, bixinbhd, by = "CT_ID", all = TRUE)
```

```{r, echo=FALSE, warning=FALSE}
rdt0 <- subset(rd, pre_post_n_13_11 == 0, select = c(id, pre_post_n_13_11, bixarea_09, dist_2009, av_time1,velototmin_n_13_11, velo_day_n_13_11, bixinbhd, age_n_13_11, d_sexef_n_13_11, alcool_nbr_n_13_11, dens_dest, road_kernel, count_stre_n_19_11, bmi_n_13_11, apvigmin_n_13_11, revenu_n_4_0, sante1an_n_4_0, sse_n_4_0, kids_n_4_0, pop_dens, b_nbhd_2009.x))
rdt1 <- subset(rd, pre_post_n_13_11 == 1, select = c(id, pre_post_n_13_11, bixarea_10, dist_2010, av_time2,velototmin_n_13_11, velo_day_n_13_11, bixinbhd, age_n_13_11, d_sexef_n_13_11, alcool_nbr_n_13_11, dens_dest, road_kernel, count_stre_n_19_11, bmi_n_13_11, apvigmin_n_13_11, revenu_n_4_0, sante1an_n_4_0, sse_n_4_0, kids_n_4_0, pop_dens, b_nbhd_2010.x))
rdt2 <- subset(rd, pre_post_n_13_11 == 2, select = c(id, pre_post_n_13_11,bixarea_11, dist_2011, av_time3,velototmin_n_13_11, velo_day_n_13_11, bixinbhd, age_n_13_11, d_sexef_n_13_11, alcool_nbr_n_13_11, dens_dest, road_kernel, count_stre_n_19_11, bmi_n_13_11, apvigmin_n_13_11, revenu_n_4_0, sante1an_n_4_0, sse_n_4_0, kids_n_4_0, pop_dens, b_nbhd_2011.x))

names(rdt0) <- c("id", "prePost", "bixArea09", "dist09", "av_time1", "veloTotMin", "veloDay", "bixiNbhd", "age", "sexF", "alcool", "denstDest", "roadKern", "countStreet", "bmi", "vigMinPA", "income", "srHealth", "srSES", "kids", "popDens", "treatment")
names(rdt1) <- c("id", "prePost", "bixArea10", "dist10",  "av_time2", "veloTotMin", "veloDay", "bixiNbhd", "age", "sexF", "alcool", "denstDest", "roadKern", "countStreet", "bmi", "vigMinPA", "income", "srHealth", "srSES", "kids", "popDens", "treatment")
names(rdt2) <- c("id", "prePost", "bixArea11", "dist11", "av_time3", "veloTotMin", "veloDay", "bixiNbhd", "age", "sexF", "alcool", "denstDest", "roadKern", "countStreet", "bmi", "vigMinPA", "income", "srHealth", "srSES", "kids", "popDens", "treatment")

rdt0$bixiNbhd <- car::recode(rdt0$bixiNbhd, 
              "0 ='Yes';
              1 = 'No'", as.factor.result=TRUE)

rdt1$bixiNbhd <- car::recode(rdt1$bixiNbhd, 
              "0 ='Yes';
              1 = 'No'", as.factor.result=TRUE)

rdt2$bixiNbhd <- car::recode(rdt2$bixiNbhd, 
              "0 ='Yes';
              1 = 'No'", as.factor.result=TRUE)
```

Variables were calculated using ArcGIS and recoded in R. 

# Outcome Variable - Minutes of Cycling in the past Week

Recoded outliers >500 minutes per week to 500

```{r, echo=FALSE, warning=FALSE}
rdt0$veloTotMin <- ifelse(rdt0$veloTotMin>500, 500, rdt0$veloTotMin)
rdt0$veloMiss <- is.na(rdt0$veloTotMin)

rdt1$veloTotMin <- ifelse(rdt1$veloTotMin>500, 500, rdt1$veloTotMin)
rdt1$veloMiss <- is.na(rdt1$veloTotMin)

rdt2$veloTotMin <- ifelse(rdt2$veloTotMin>500, 500, rdt2$veloTotMin)
rdt2$veloMiss <- is.na(rdt2$veloTotMin)
```

### Pre-Implementation
```{r, echo=TRUE, warning=FALSE}
psych::describe(rdt0$veloTotMin, skew = FALSE)
# Pre-implementation histogram of minutes of cycling in the past week
histogramVelo <- ggplot(rdt0, aes(veloTotMin)) +
  geom_histogram()
plot(histogramVelo)
```

### Season 1
```{r, echo=TRUE, warning=FALSE}
psych::describe(rdt1$veloTotMin, skew = FALSE)
# Season 1 histogram of minutes of cycling in the past week
histogramVelot1 <- ggplot(rdt1, aes(veloTotMin)) +
  geom_histogram()
plot(histogramVelot1)
```

### Season 2
```{r, echo=TRUE, warning=FALSE}
library(ggplot2)

psych::describe(rdt2$veloTotMin, skew = FALSE)
# Season 2 histogram of minutes of cycling in the past week
histogramVelot2 <- ggplot(rdt2, aes(veloTotMin)) +
  geom_histogram()
plot(histogramVelot2)
```

# Assignment variable (Distance to the disconuity of bikeshare stations)

Checking the assignment variable and converting so negative values are outside of the bikeshare implementation area and positive values are inside the bikeshare implementation area. 

```{r, warning=FALSE, include=FALSE}
### Convert Assignment 
psych::describe(rdt0$dist09)
table(rdt0$bixArea09)
rdt0$assignment1 <- rdt0$dist09*100

rdt0$assignment <- ifelse(rdt0$bixArea09==1, rdt0$assignment1, (rdt0$assignment1*-1))
rdt0$dAssign <- ifelse(rdt0$assignment>=0, 1, 0)

table(rdt0$dAssign)

psych::describe(rdt0$assignment)
rdt0$assignMiss <- is.na(rdt0$assignment)
```

## Distribution of the assignment variable

### Pre-Implementation 

```{r, echo=TRUE, warning=FALSE}
histogramAssign <- ggplot(rdt0, aes(assignment)) +
  geom_histogram(binwidth = 0.5)
plot(histogramAssign)
```

Subset the data so only those with +- 2Km from the cut off are included.

```{r, echo=TRUE, warning=FALSE}
rdt0 <- subset(rdt0, assignment>=-2)
```

#### Plot and table for residing in bikeshare neighbourhood versus inside bikeshare zone

```{r}
fuzzy_plot1 <- ggplot(rdt0, aes(x = assignment, y = veloTotMin)) + 
            geom_point(aes(colour=factor(bixiNbhd)), shape = 1) + 
            geom_point(aes(colour=factor(bixiNbhd)), shape = 1) + 
            geom_vline(xintercept = 0) + 
            scale_colour_manual(values = c("black", "gray90")) +  
            scale_fill_manual(values = c("black", "gray90")) +  
            theme(axis.line = element_line(colour = "black"),
                panel.background = element_blank(),
                axis.title=element_text(size=16),
                text=element_text(size=14)) + 
            xlab("Distance") +
            ylab("Minutes of cycling per week")
plot(fuzzy_plot1)

table(rdt0$dAssign, rdt0$bixiNbhd)
```

```{r}
histogramAssign <- ggplot(rdt0, aes(assignment)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.05, colour="black", fill="white") + 
  geom_density(alpha=.6, fill="grey") + 
  geom_vline(xintercept = 0) + 
  expand_limits(y = 0) + 
        scale_colour_manual(values = c("black", "grey")) +  
        scale_fill_manual(values = c("black", "grey")) +  
  theme(axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        axis.title=element_text(size=16),
        text=element_text(size=14)) + 
        xlab("Distance for Bikeshare Station") +
        ylab("Density")
plot(histogramAssign)

ggsave("histogramAssign.pdf", histogramAssign, dpi = 300)
```

### Season 1 

```{r, include=FALSE, warning=FALSE}
### Convert Assignment 
rdt1$assignment1 <- rdt1$dist10*100
rdt1$assignment <- ifelse(rdt1$bixArea10==1, rdt1$assignment1, (rdt1$assignment1*-1))
rdt1$dAssign<- ifelse(rdt1$assignment>=0, 1, 0)

psych::describe(rdt1$assignment)
rdt1$assignMiss <- is.na(rdt1$assignment)
```

```{r, echo=TRUE, warning=FALSE}
rdt1 <- subset(rdt1, assignment>=-2)
```

#### Plot and table for residing in bikeshare neighbourhood versus inside bikeshare zone

```{r}
fuzzy_plot2 <- ggplot(rdt1, aes(x = assignment, y = veloTotMin)) + 
            geom_point(aes(colour=factor(bixiNbhd)), shape = 1) + 
            geom_point(aes(colour=factor(bixiNbhd)), shape = 1) + 
            geom_vline(xintercept = 0) + 
            scale_colour_manual(values = c("black", "gray90")) +  
            scale_fill_manual(values = c("black", "gray90")) +  
            theme(axis.line = element_line(colour = "black"),
                panel.background = element_blank(),
                axis.title=element_text(size=16),
                text=element_text(size=14)) + 
            xlab("Distance") +
            ylab("Minutes of cycling per week")
plot(fuzzy_plot2)

table(rdt1$dAssign, rdt1$bixiNbhd)
```


```{r}
histogramAssign1 <- ggplot(rdt1, aes(assignment)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.05, colour="black", fill="white") + 
  geom_density(alpha=.6, fill="grey") + 
  geom_vline(xintercept = 0) + 
  expand_limits(y = 0) + 
        scale_colour_manual(values = c("black", "grey")) +  
        scale_fill_manual(values = c("black", "grey")) +  
  theme(axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        axis.title=element_text(size=16),
        text=element_text(size=14)) + 
        xlab("Distance for Bikeshare Station") +
        ylab("Density")
plot(histogramAssign1)

ggsave("histogramAssign1.pdf", histogramAssign1, dpi = 300)
```

### Season 2

```{r, include=FALSE, warning=FALSE}
### Convert Assignment 
rdt2$assignment1 <- rdt2$dist11*100
rdt2$assignment <- ifelse(rdt2$bixArea11==1, rdt2$assignment1, (rdt2$assignment1*-1))
rdt2$dAssign<- ifelse(rdt2$assignment>=0, 1, 0)
psych::describe(rdt2$assignment)
rdt2$assignMiss <- is.na(rdt2$assignment)
```

```{r, echo=TRUE, warning=FALSE}
rdt2 <- subset(rdt2, assignment>=-2)
```

#### Plot and table for residing in bikeshare neighbourhood versus inside bikeshare zone

```{r}
fuzzy_plot2 <- ggplot(rdt1, aes(x = assignment, y = veloTotMin)) + 
            geom_point(aes(colour=factor(bixiNbhd)), shape = 1) + 
            geom_point(aes(colour=factor(bixiNbhd)), shape = 1) + 
            geom_vline(xintercept = 0) + 
            scale_colour_manual(values = c("black", "gray90")) +  
            scale_fill_manual(values = c("black", "gray90")) +  
            theme(axis.line = element_line(colour = "black"),
                panel.background = element_blank(),
                axis.title=element_text(size=16),
                text=element_text(size=14)) + 
            xlab("Distance") +
            ylab("Minutes of cycling per week")
plot(fuzzy_plot2)

table(rdt1$dAssign, rdt1$bixiNbhd)
```

```{r}
histogramAssign2 <- ggplot(rdt2, aes(assignment)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.05, colour="black", fill="white") + 
  geom_density(alpha=.6, fill="grey") + 
  geom_vline(xintercept = 0) + 
  expand_limits(y = 0) + 
        scale_colour_manual(values = c("black", "grey")) +  
        scale_fill_manual(values = c("black", "grey")) +  
  theme(axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        axis.title=element_text(size=16),
        text=element_text(size=14)) + 
        xlab("Distance for Bikeshare Station") +
        ylab("Density")
plot(histogramAssign2)

ggsave("histogramAssign2.pdf", histogramAssign2, dpi = 300)
```

## Treatment variable by outcome

### Pre-implementation
```{r, echo=FALSE, warning=FALSE}
sumFun <- function(x, ...){
  c(m=mean(x, ...), Stand_Dev=sd(x, ...))}

veloDesc <- summaryBy(veloTotMin ~ bixArea09, data = rdt0, FUN = sumFun, 
                     na.rm=TRUE)
head(veloDesc)
```

### Season 1
```{r, echo=FALSE, warning=FALSE}
veloDesct1 <- summaryBy(veloTotMin ~ bixArea10, data = rdt1, FUN = sumFun, 
                     na.rm=TRUE)
print(head(veloDesct1))
```

### Season 2
```{r, echo=FALSE, warning=FALSE}
veloDesct1 <- summaryBy(veloTotMin ~ bixArea11, data = rdt2, FUN = sumFun, 
                     na.rm=TRUE)
print(head(veloDesct1))
```

# 1.	Graphed the relationship between the assignment and treatment variable (Figure 2)

## Figure 2 - Relationship between the assignment (distance) and treatment (living in a bikeshare neighbourhood) variables 

### 2A. Pre-implentation

```{r, echo=TRUE, warning=FALSE}
table(rdt0$treatment, rdt0$dAssign)
```

### 2B. Season 1

```{r, echo=FALSE, warning=FALSE}
table(rdt1$treatment, rdt1$dAssign)
```

### 2C. Season 2

```{r, echo=FALSE, warning=FALSE}
table(rdt2$treatment, rdt2$dAssign)
```

# 2.	Graphed the assignment by outcome variable scatterplot with linear and empirically estimated regression functions (Figure 3)

## Figure 3. Assignment by outcome variable scatterplot with linear and empirically estimated regression functions

### 3A. Pre-implementation

```{r}
rdPlot1 <- ggplot(rdt0, aes(x = assignment, y = veloTotMin, fill=factor(dAssign))) + 
            geom_point(aes(colour=factor(dAssign)), alpha = 1/2) + 
            geom_smooth(aes(fill=factor(dAssign)), method = "lm", se=FALSE, colour="black") + 
            geom_smooth(aes(fill=factor(dAssign)), linetype="solid", colour="#FFFFFF") + 
            geom_vline(xintercept = 0) + 
            scale_colour_manual(values = c("black", "#333333")) +  
            scale_fill_manual(values = c("black", "#333333")) +  
            theme(axis.line = element_line(colour = "black"),
                panel.background = element_blank(),
                axis.title=element_text(size=16),
                text=element_text(size=14)) + 
            xlab("Distance") +
            ylab("Minutes of cycling per week")
print(rdPlot1)

ggsave("rdMain.jpg", rdPlot1, dpi = 300)
```

### 3B. Season 1
```{r}
rdPlot1t1 <- ggplot(rdt1, aes(x = assignment, y = veloTotMin, fill=factor(dAssign))) + 
            geom_point(aes(colour=factor(dAssign)), alpha = 1/2) + 
            geom_smooth(aes(fill=factor(dAssign)), method = "lm", se=FALSE, colour="black") + 
            geom_smooth(aes(fill=factor(dAssign)), linetype="solid", colour="#FFFFFF") + 
            geom_vline(xintercept = 0) + 
            scale_colour_manual(values = c("black", "#333333")) +  
            scale_fill_manual(values = c("black", "#333333")) +  
            theme(axis.line = element_line(colour = "black"),
                panel.background = element_blank(),
                axis.title=element_text(size=16),
                text=element_text(size=14)) + 
            xlab("Distance") +
            ylab("Minutes of cycling per week")
print(rdPlot1t1)

ggsave("rdMaint1.jpg", rdPlot1t1, dpi = 300)
```

### 3C. Season 2

```{r}
rdPlot1t2 <- ggplot(rdt2, aes(x = assignment, y = veloTotMin, fill=factor(dAssign))) + 
            geom_point(aes(colour=factor(dAssign)), alpha = 1/2) + 
            geom_smooth(aes(fill=factor(dAssign)), method = "lm", se=FALSE, colour="black") + 
            geom_smooth(aes(fill=factor(dAssign)), linetype="solid", colour="#FFFFFF") + 
            geom_vline(xintercept = 0) + 
            scale_colour_manual(values = c("black", "#333333")) +  
            scale_fill_manual(values = c("black", "#333333")) +  
            theme(axis.line = element_line(colour = "black"),
                panel.background = element_blank(),
                axis.title=element_text(size=16),
                text=element_text(size=14)) + 
            xlab("Distance") +
            ylab("Minutes of cycling per week")
print(rdPlot1t2)

ggsave("rdMaint2.jpg", rdPlot1t2, dpi = 300)
```

## Figure 3. Default parameters based on [rdrobust package](https://journal.r-project.org/archive/2015-1/cattaneo-calonico-titiunik.pdf)

### Pre-implementation
```{r, echo=TRUE, warning=FALSE}
rdplot(y = rdt0$veloTotMin, x = rdt0$assignment, c=0, y.label = "Minutes of cycling per week", x.label = "Distance")
```

### Season 1
```{r, echo=FALSE, warning=FALSE}
rdplot(y = rdt1$veloTotMin, x = rdt1$assignment, c=0, y.label = "Minutes of cycling per week", x.label = "Distance")
```

### Season 2
```{r, echo=FALSE, warning=FALSE}
rdplot(y = rdt2$veloTotMin, x = rdt2$assignment, c=0, y.label = "Minutes of cycling per week", x.label = "Distance")
```

## Descriptive Statistics for each survey period 
```{r, include=FALSE, warning=FALSE}
### Pre-Implementation
lmt0 <- lm(veloTotMin ~ assignment, data=rdt0, na.action = na.exclude)
rdt0$predRDt0 <- fitted(lmt0)
rdt0$predRDt0 <- is.na(rdt0$predRDt0)
rdt0 <- filter(rdt0, predRDt0==FALSE)

### Season 1
lmt1 <- lm(veloTotMin ~ assignment, data=rdt1, na.action = na.exclude)
rdt1$predRDt1 <- fitted(lmt1)
rdt1$predRDt1 <- is.na(rdt1$predRDt1)
rdt1 <- filter(rdt1, predRDt1==FALSE)

### Season 2
lm <- lm(veloTotMin ~ assignment, data=rdt2, na.action = na.exclude)
rdt2$predRDt2 <- fitted(lm)
rdt2$predRDt2 <- is.na(rdt2$predRDt2)
rdt2 <- filter(rdt2, predRDt2==FALSE)
```

### Pre-Implementation
```{r, echo=FALSE, warning=FALSE}
rdt0 %>%
    summarise(m.age = mean(age, na.rm=TRUE),
              sd.age = sd(age, na.rm=TRUE),
              m.alcool = mean(alcool, na.rm=TRUE),
              sd.alcool = sd(alcool, na.rm=TRUE),
              m.bmi = mean(bmi, na.rm=TRUE),
              sd.bmi = sd(bmi, na.rm=TRUE),
              m.popDens = mean(popDens, na.rm=TRUE),
              sd.popDens = sd(popDens, na.rm=TRUE),
              m.kids = mean(kids, na.rm=TRUE),
              sd.kids = sd(kids, na.rm=TRUE),
              sexFPct = mean(sexF, na.rm=TRUE),
              m.veloTotMin = mean(veloTotMin, na.rm=TRUE),
              sd.pveloTotMin = sd(veloTotMin, na.rm=TRUE),
              total = n())
```

### Season 1
```{r, echo=FALSE, warning=FALSE}
rdt1 %>%
    summarise(m.age = mean(age, na.rm=TRUE),
              sd.age = sd(age, na.rm=TRUE),
              m.alcool = mean(alcool, na.rm=TRUE),
              sd.alcool = sd(alcool, na.rm=TRUE),
              m.bmi = mean(bmi, na.rm=TRUE),
              sd.bmi = sd(bmi, na.rm=TRUE),
              m.popDens = mean(popDens, na.rm=TRUE),
              sd.popDens = sd(popDens, na.rm=TRUE),
              m.kids = mean(kids, na.rm=TRUE),
              sd.kids = sd(kids, na.rm=TRUE),
              sexFPct = mean(sexF, na.rm=TRUE),
              m.veloTotMin = mean(veloTotMin, na.rm=TRUE),
              sd.pveloTotMin = sd(veloTotMin, na.rm=TRUE),
              total = n())
```

### Season 2
```{r, echo=FALSE, warning=FALSE}
rdt2 %>%
    summarise(m.age = mean(age, na.rm=TRUE),
              sd.age = sd(age, na.rm=TRUE),
              m.alcool = mean(alcool, na.rm=TRUE),
              sd.alcool = sd(alcool, na.rm=TRUE),
              m.bmi = mean(bmi, na.rm=TRUE),
              sd.bmi = sd(bmi, na.rm=TRUE),
              m.popDens = mean(popDens, na.rm=TRUE),
              sd.popDens = sd(popDens, na.rm=TRUE),
              m.kids = mean(kids, na.rm=TRUE),
              sd.kids = sd(kids, na.rm=TRUE),
              sexFPct = mean(sexF, na.rm=TRUE),
              m.veloTotMin = mean(veloTotMin, na.rm=TRUE),
              sd.pveloTotMin = sd(veloTotMin, na.rm=TRUE),
              total = n())
```

# 3. Examined the averages of selected covariates on either side of the cut-off (Table 1)

## Table 1. Averages of selected covariates on either side of the cut-off

### Pre-Implementation

```{r, echo=FALSE, warning=FALSE}
table1 <- rdt0 %>%
  group_by(dAssign) %>%
    summarise(m.age = mean(age, na.rm=TRUE),
              sd.age = sd(age, na.rm=TRUE),
              m.alcool = mean(alcool, na.rm=TRUE),
              sd.alcool = sd(alcool, na.rm=TRUE),
              m.bmi = mean(bmi, na.rm=TRUE),
              sd.bmi = sd(bmi, na.rm=TRUE),
              m.popDens = mean(popDens, na.rm=TRUE),
              sd.popDens = sd(popDens, na.rm=TRUE),
              m.kids = mean(kids, na.rm=TRUE),
              sd.kids = sd(kids, na.rm=TRUE),
              m.sexF = mean(sexF, na.rm=TRUE),
              sd.sexF = sd(sexF, na.rm=TRUE),
              m.veloTotMin = mean(veloTotMin, na.rm=TRUE),
              sd.pveloTotMin = sd(veloTotMin, na.rm=TRUE),
              total = n())
print(table1, width = Inf)
write.csv(table1, "t0Descriptives.csv")
```

#### Income
```{r, echo=FALSE, warning=FALSE}
rdt0$rincome <- car::recode(rdt0$income, 
              "1:2='1 - <20k';
              3:4='2 - 20-49k';
              5:6='3 - 50-99k';
              7:9='4 - 100k+';
              99=NA", as.factor.result=TRUE)
t_inct0 <- table(rdt0$dAssign, rdt0$rincome)
cbind(t_inct0, prop.table(t_inct0, 1))
```

#### Self-Rated Health
```{r, echo=FALSE, warning=FALSE}
rdt0$rSRHealth <- car::recode(rdt0$srHealth, 
              "1:2='Excellent';
              3:5='Bad/Good';
              9=NA", as.factor.result=TRUE)
t_SHRt0 <- table(rdt0$dAssign, rdt0$rSRHealth)
cbind(t_SHRt0, prop.table(t_SHRt0, 1))
```

### Season 1
```{r, echo=FALSE, warning=FALSE}
table2 <- rdt1 %>%
  group_by(dAssign) %>%
    summarise(m.age = mean(age, na.rm=TRUE),
              sd.age = sd(age, na.rm=TRUE),
              m.alcool = mean(alcool, na.rm=TRUE),
              sd.alcool = sd(alcool, na.rm=TRUE),
              m.bmi = mean(bmi, na.rm=TRUE),
              sd.bmi = sd(bmi, na.rm=TRUE),
              m.popDens = mean(popDens, na.rm=TRUE),
              sd.popDens = sd(popDens, na.rm=TRUE),
              m.kids = mean(kids, na.rm=TRUE),
              sd.kids = sd(kids, na.rm=TRUE),
              m.sexF = mean(sexF, na.rm=TRUE),
              sd.sexF = sd(sexF, na.rm=TRUE),
              m.veloTotMin = mean(veloTotMin, na.rm=TRUE),
              sd.pveloTotMin = sd(veloTotMin, na.rm=TRUE),
              total = n())
print(table2, width = Inf)
write.csv(table2, "t1Descriptives.csv")
```

#### Income
```{r, echo=FALSE, warning=FALSE}
rdt1$rincome <- car::recode(rdt1$income, 
              "1:2='1 - <20k';
              3:4='2 - 20-49k';
              5:6='3 - 50-99k';
              7:9='4 - 100k+';
              99=NA", as.factor.result=TRUE)
t_inct1 <- table(rdt1$dAssign, rdt1$rincome)
cbind(t_inct1, prop.table(t_inct1, 1))
```

#### Self-Rated Health
```{r, echo=FALSE, warning=FALSE}
rdt1$rSRHealth <- car::recode(rdt1$srHealth, 
              "1:2='Excellent';
              3:5='Bad/Good';
              9=NA", as.factor.result=TRUE)
t_SRHt1 <- table(rdt1$dAssign, rdt1$rSRHealth)
cbind(t_SRHt1, prop.table(t_SRHt1, 1))
```

### Season 2
```{r, echo=FALSE, warning=FALSE}
table3 <- rdt2 %>%
  group_by(dAssign) %>%
    summarise(m.age = mean(age, na.rm=TRUE),
              sd.age = sd(age, na.rm=TRUE),
              m.alcool = mean(alcool, na.rm=TRUE),
              sd.alcool = sd(alcool, na.rm=TRUE),
              m.bmi = mean(bmi, na.rm=TRUE),
              sd.bmi = sd(bmi, na.rm=TRUE),
              m.popDens = mean(popDens, na.rm=TRUE),
              sd.popDens = sd(popDens, na.rm=TRUE),
              m.kids = mean(kids, na.rm=TRUE),
              sd.kids = sd(kids, na.rm=TRUE),
              m.sexF = mean(sexF, na.rm=TRUE),
              sd.sexF = sd(sexF, na.rm=TRUE),
              m.veloTotMin = mean(veloTotMin, na.rm=TRUE),
              sd.pveloTotMin = sd(veloTotMin, na.rm=TRUE),
              total = n())
print(table3, width = Inf)
write.csv(table3, "t2Descriptives.csv")
```

#### Income

```{r, echo=FALSE, warning=FALSE}
rdt2$rincome <- car::recode(rdt2$income, 
              "1:2='1 - <20k';
              3:4='2 - 20-49k';
              5:6='3 - 50-99k';
              7:9='4 - 100k+';
              99=NA", as.factor.result=TRUE)
t_inct2 <- table(rdt2$dAssign, rdt2$rincome)
cbind(t_inct2, prop.table(t_inct2, 1))
```

#### Self-Rated Health

```{r, echo=FALSE, warning=FALSE}
rdt2$rSRHealth <- car::recode(rdt2$srHealth, 
              "1:2='Excellent';
              3:5='Bad/Good';
              9=NA", as.factor.result=TRUE)
t_SRHt2 <- table(rdt2$dAssign, rdt2$rSRHealth)
cbind(t_SRHt2, prop.table(t_SRHt2, 1))
```

# 4. Examined whether the results were sensitive to regression specification and bandwidth selection (Table 2)

## Table 2: Estimating the Regressions

```{r, echo=FALSE, warning=FALSE}
url_robust <- "https://raw.githubusercontent.com/IsidoreBeautrelet/economictheoryblog/master/robust_summary.R"
eval(parse(text = getURL(url_robust, ssl.verifypeer = FALSE)),
     envir=.GlobalEnv)
```

### Pre-Implementation

#### Pre-Implementation - Linear regression with robust standard errors
```{r, echo=TRUE, warning=FALSE}
lmt0 <- lm(veloTotMin ~ dAssign + assignment, data=rdt0)
cbind(coef = coef(lmt0, robust=TRUE), confint(lmt0, robust=TRUE))

table(rdt0$dAssign)
```

#### Pre-Implementation - Robust RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c=0, kernel= "tri", all=TRUE)
```

#### Pre-Implementation - Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

#### Pre-Implementation - Robust  RD regression with epanechnikov kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c=0, kernel="epa", all=TRUE)
```

#### Pre-Implementation - Robust  RD regression with epanechnikov kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c=0, bwselect="msetwo", kernel="epa", all=TRUE)
```

#### Pre-Implementation - Robust  RD regression with uniform kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c=0, kernel="uni", all=TRUE)
```

#### Pre-Implementation - Robust  RD regression with uniform kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c=0, bwselect="msetwo", kernel="uni", all=TRUE)
```

### Season 1

#### Season 1 - Linear regression with robust standard errors
```{r, echo=TRUE, warning=FALSE}
lmt1 <- lm(veloTotMin ~ dAssign + assignment, data=rdt1)
cbind(coef = coef(lmt1, robust=TRUE), confint(lmt1, robust=TRUE))

table(rdt1$dAssign)
```

#### Season 1 - Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0, kernel= "tri", all=TRUE)
```

#### Season 1 - Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

#### Season 1 - Robust  RD regression with epanechnikov kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0, kernel="epa", all=TRUE)
```

#### Season 1 - Robust  RD regression with epanechnikov kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0, bwselect="msetwo", kernel="epa", all=TRUE)
```

#### Season 1 - Robust  RD regression with uniform kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0, kernel="uni", all=TRUE)
```

#### Season 1 - Robust  RD regression with uniform kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0, bwselect="msetwo", kernel="uni", all=TRUE)
```

### Season 2

#### Season 2 - Linear regression with robust standard errors
```{r, echo=TRUE, warning=FALSE}
lmt2 <- lm(veloTotMin ~ dAssign + assignment, data=rdt2)
cbind(coef = coef(lmt2, robust=TRUE), confint(lmt2, robust=TRUE))

table(rdt2$dAssign)
```

#### Season 2 - Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0, kernel= "tri", all=TRUE)
```

#### Season 2 - Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

#### Season 2 - Robust  RD regression with epanechnikov kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0, kernel="epa", all=TRUE)
```

#### Season 2 - Robust  RD regression with epanechnikov kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0, bwselect="msetwo", kernel="epa", all=TRUE)
```

#### Season 2 - Robust  RD regression with uniform kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0, kernel="uni", all=TRUE)
```

#### Season 2 - Robust  RD regression with uniform kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0, bwselect="msetwo", kernel="uni", all=TRUE)
```

# 5. Examine whether the outcome is discontinuous at other values of the forcing variable 

### Pre-Implementation

```{r, echo=TRUE, warning=FALSE}
### Median of assignment variable
median(rdt0$assignment)

rdplot(y = rdt0$veloTotMin, x = rdt0$assignment, c = 0.1139, y.label = "Minutes of cycling per week", x.label = "Distance")
```

#### Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)

```{r, echo=FALSE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c = 0.1139, kernel = "tri", all = TRUE)
```

  

#### Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=FALSE, warning=FALSE}
rdrobust(rdt0$veloTotMin, rdt0$assignment, c = 0.1139, bwselect ="msetwo", kernel = "tri", all=TRUE)
```

  

### Season 1

```{r, echo=TRUE, warning=FALSE}
### Median of assignment variable
median(rdt1$assignment)

rdplot(y = rdt1$veloTotMin, x = rdt1$assignment, c=0.196, y.label = "Minutes of cycling per week", x.label = "Distance")
```

  

## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0.196, kernel= "tri", all=TRUE)
```

  

## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt1$veloTotMin, rdt1$assignment, c=0.196, bwselect="msetwo", kernel= "tri", all=TRUE)
```

  

### Season 2

```{r, echo=TRUE, warning=FALSE}
### Median of assignment variable
median(rdt2$assignment)

rdplot(y = rdt2$veloTotMin, x = rdt2$assignment, c=0.3841, y.label = "Minutes of cycling per week", x.label = "Distance")
```

  

## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0.3841, kernel= "tri", all=TRUE)
```

  

## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
```{r, echo=TRUE, warning=FALSE}
rdrobust(rdt2$veloTotMin, rdt2$assignment, c=0.3841, bwselect="msetwo", kernel= "tri", all=TRUE)
```

  

# 6.	Examined whether jumps existing for population density and number of kids in the home.

### Pre-Implementation

#### Pre-Implementation - Population Density
```{r, echo=TRUE, warning=FALSE}
rdplot(y = rdt0$popDens, x = rdt0$assignment, c=0, y.label = "Population Density", x.label = "Distance")
```

  

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
rdrobust(rdt0$popDens, rdt0$assignment, c=0, kernel= "tri", all=TRUE)
```

  

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
rdrobust(rdt0$popDens, rdt0$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

  

#### Pre-Implementation - Number of Kids
```{r, echo=TRUE, warning=FALSE}
rdplot(y = rdt0$kids, x = rdt0$assignment, c=0, y.label = "Number of Kids in Home", x.label = "Distance")
```

  

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
rdrobust(rdt0$kids, rdt0$assignment, c=0, kernel= "tri", all=TRUE)
```

  

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
rdrobust(rdt0$kids, rdt0$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

  

### Season 1

#### Season 1 - Population Density
```{r, echo=TRUE, warning=FALSE}
rdplot(y = rdt1$popDens, x = rdt1$assignment, c=0, y.label = "Population Density", x.label = "Distance")
```

  

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
rdrobust(rdt1$popDens, rdt1$assignment, c=0, kernel= "tri", all=TRUE)
```

  

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
rdrobust(rdt1$popDens, rdt1$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

  

#### Season 1 - Number of Kids
```{r, echo=TRUE, warning=FALSE}
rdplot(y = rdt1$kids, x = rdt1$assignment, c=0, y.label = "Number of Kids in Home", x.label = "Distance")
```

 

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
rdrobust(rdt1$kids, rdt1$assignment, c=0, kernel= "tri", all=TRUE)
```

 

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
rdrobust(rdt1$kids, rdt1$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

 

### Season 2

#### Season 2 - Population Density
```{r, echo=TRUE, warning=FALSE}
rdplot(y = rdt2$popDens, x = rdt2$assignment, c=0, y.label = "Population Density", x.label = "Distance")
```

 

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
rdrobust(rdt2$popDens, rdt2$assignment, c=0, kernel= "tri", all=TRUE)
```

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
rdrobust(rdt2$popDens, rdt2$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

#### Season 2 - Number of Kids
```{r, echo=TRUE, warning=FALSE}
rdplot(y = rdt2$kids, x = rdt2$assignment, c=0, y.label = "Number of Kids in Home", x.label = "Distance")
```

 

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and one common MSE-optimal bandwidth selector (mserd)
rdrobust(rdt2$kids, rdt2$assignment, c=0, kernel= "tri", all=TRUE)
```

 

```{r, echo=TRUE, warning=FALSE}
## Robust  RD regression with triangular kernel and two different MSE-optimal bandwidth selectors (msetwo)
rdrobust(rdt2$kids, rdt2$assignment, c=0, bwselect="msetwo", kernel= "tri", all=TRUE)
```

# The end








